Paper Plots V1

### 2025-01-22 Rmd/paper_plots/paper_plots_1.1.Rmd
add more grid scenarios

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F, results = "hide", fig.width = 8.5, fig.height = 5, dpi = 600)
library(tidytable)
library(data.table)
library(reshape2)
library(ggplot2)
library(knitr)
opts_knit$set(eval.after = "fig.cap")
options(scipen = 5)
```

@@

@@

@@

### Boxplots
```{r}
df2 %>% 
  tidytable::mutate(ISS.diff = (df2$ISS[df2$scenario=="N_1.00"]) - ISS,
                    ISS.error = (ISS - df2$ISS[df2$scenario=="N_1.00"])/df2$ISS[df2$scenario=="N_1.00"],
                    type = "haul",
                    .by = scenario) -> df3.2

@@

df4 %>% 
  ggplot(aes(x = scenario, y = ISS.error)) +
  geom_boxplot(aes(fill = type)) +
  labs(x = "Scenario", y = "ISSB") +
  theme_classic() +
  theme(legend.position = c(0.5, 0.9))

@@

df4 %>% 
  ggplot(aes(x = scenario, y = ISS.error)) +
  geom_boxplot(aes(fill = type))

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F, results = "hide", fig.width = 8.5, fig.height = 5, dpi = 600)
library(tidytable)
library(data.table)
library(reshape2)
library(ggplot2)
library(knitr)
library(stringr)
library(patchwork)
opts_knit$set(eval.after = "fig.cap")
options(scipen = 5)
```

@@

out_1.2 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_1.2_ISS_1iters_output_2025-01-10.RDS")

@@

### All together TRIPS TOO 4 panel

plot(out_1.2$length$iss$YEAR, out_1.2$length$iss$ntps, ylim = c(0, 1000), ylab = "Number of Trips", type = "l", cex.lab = 1.3, xaxt = "n", xlab = "")

plot(out_1.1$length$iss$YEAR, out_1.1$length$iss$nss, type = "l", ylab = "nominal sample size", cex.lab = 1.3, xlab = "year")

### All together TRIPS TOO 3 panel

# par(mfrow = c(4,1), mar = c(0,0,0,0), oma = c(2, 4, 2, .5), mgp = c(2, .6, 0))
# par(mfrow = c(3,1), mar = c(1.5, 3.1, 0, .5), mgp = c(2, .6, 0))
par(mfrow = c(3,1), mar = c(0,3.1,0,0), oma = c(2, 0, 2, .5), mgp = c(2, .6, 0))
plot(out_1.1$length$iss$YEAR, out_1.1$length$iss$iss, type = "l", ylab = "ISS", xaxt = "n", ylim = c(0, 15000)) 
lines(assessment_2023_iss$year, assessment_2023_iss$iss, col = "blue")
lines(out_1.1$length$iss$YEAR, out_1.1$length$iss$nhls, col = "red")
lines(out_1.2$length$iss$YEAR, out_1.2$length$iss$ntps, col = "green")
legend("topleft", lty = c(1,1,1), col = c("black", "blue", "red"), legend = c("ISSB", "ISSA", "number of hauls"))

@@

### Boxplots Haul and Trip
```{r}
df2 %>% 
  tidytable::mutate(ISS.diff = (df2$ISS[df2$scenario=="N_1.00"]) - ISS,
                    ISS.error = (ISS - df2$ISS[df2$scenario=="N_1.00"])/df2$ISS[df2$scenario=="N_1.00"],
                    type = "haul",
                    .by = scenario) -> df3.2

@@

df4 %>% 
  ggplot(aes(x = scenario, y = ISS.error*100)) +
  geom_boxplot(aes(fill = type)) +
  labs(x = "Scenario", y = "ISSB % Error") +
  theme_classic() +
  theme(legend.position = c(0.5, 0.9)) +
  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
  geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
  scale_y_continuous(breaks = seq(-100, 120, by = 10), limits = c(-100, 120))

# Stats
df4 %>% filter(type=="trip", scenario=="N_0.25") %>% pull(ISS.error) %>% median
df4 %>% filter(type=="trip", scenario=="N_2.00") %>% pull(ISS.error) %>% median
df4 %>% filter(type=="haul", scenario=="N_0.25") %>% pull(ISS.error) %>% median
df4 %>% filter(type=="haul", scenario=="N_2.00") %>% pull(ISS.error) %>% median

@@

df4 %>% 
  ggplot(aes(x = scenario, y = ISS.error*100)) +
  geom_boxplot(aes(fill = type)) +
  labs(x = "Scenario", y = "ISSB % Error") +
  theme_classic() +
  theme(legend.position = c(0.5, 0.9)) +
  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
  geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
  scale_y_continuous(breaks = seq(-100, 120, by = 10), limits = c(-100, 120))

### Boxplots samples

### Validate N=20 assumption
is assuming n=20 when the median is 20 for 1999-2023 valid to make a valid control? How well do they match?
```{r}

out_22.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_22.1_ISS_200_iters_2024-12-25.RDS")

plot(out_22.1$samples_20$expansion_haul_month_numbers$length$iss$iss, ylim = c(0, 13000))
lines(out_1.1$length$iss$iss[out_1.1$length$iss$YEAR %in% 1999:2023], col = "blue")

### Boxplots Together 1977-2023
```{r}

out_21.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_21.1_ISS_200_iters_2024-12-23.RDS")

year = out_21.1$samples_1$length$iss$YEAR
proportion_global = c(0.25, 0.50, 0.75, 1.25, 1.50, 1.75, 2.00)
type_global = list("trip", "haul")
type_names_global = c("trip", "haul")

df = tidytable(year = year,
               N_1 = out_21.1$samples_1$length$iss$iss,
               N_5 = out_21.1$samples_5$length$iss$iss,
               N_10 = out_21.1$samples_10$length$iss$iss,
               N_15 = out_21.1$samples_15$length$iss$iss,
               N_20 = out_21.1$samples_20$length$iss$iss,
               N_25 = out_21.1$samples_25$length$iss$iss,
               N_30 = out_21.1$samples_30$length$iss$iss,
               N_35 = out_21.1$samples_35$length$iss$iss)

ggplot(data = df2, aes(x = year, y = ISS, group = scenario, colour = scenario)) +
  geom_line() +
  labs(x = "Year", y = "ISS") +
  geom_point() +
  ylim(0, 17000)

df2 %>% 
  tidytable::mutate(ISS.diff = (df2$ISS[df2$scenario=="N_20"]) - ISS,
                    ISS.error = (ISS - df2$ISS[df2$scenario=="N_20"])/df2$ISS[df2$scenario=="N_20"],
                    type = "sample",
                    .by = scenario) %>% 
  tidytable::filter(year %in% 1999:2023)-> df3.2

df3.2 %>% 
  ggplot(aes(x = scenario, y = ISS.error*100)) +
  geom_boxplot(aes(fill = type)) +
  labs(x = "Scenario", y = "ISSB % Error") +
  theme_classic() +
  theme(legend.position = c(0.5, 0.2)) +
  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
  geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
  scale_y_continuous(breaks = seq(-100, 120, by = 10))

### Samples VS Expantion. Boxplots Together 1999-2023
```{r, fig.width=8}

out_22.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_22.1_ISS_200_iters_2024-12-25.RDS")

year = out_22.1$samples_1$expansion_NULL$length$iss$YEAR
samples_global = c(1, 5, 10, 15, 20, 25, 30, 35)
expansion_global = list(NULL, "haul_numbers", c("haul_numbers", "month_numbers"))
expansion_names_global = c("NULL", "haul_numbers", c("haul_month_numbers"))

df = tidytable(year = year,
               N1_Enone = out_22.1$samples_1$expansion_NULL$length$iss$iss,
               N5_Enone = out_22.1$samples_5$expansion_NULL$length$iss$iss,
               N10_Enone = out_22.1$samples_10$expansion_NULL$length$iss$iss,
               N15_Enone = out_22.1$samples_15$expansion_NULL$length$iss$iss,
               N20_Enone = out_22.1$samples_20$expansion_NULL$length$iss$iss,
               N25_Enone = out_22.1$samples_25$expansion_NULL$length$iss$iss,
               N30_Enone = out_22.1$samples_30$expansion_NULL$length$iss$iss,
               N35_Enone = out_22.1$samples_35$expansion_NULL$length$iss$iss,
               N1_Emedium = out_22.1$samples_1$expansion_haul_numbers$length$iss$iss,
               N5_Emedium = out_22.1$samples_5$expansion_haul_numbers$length$iss$iss,
               N10_Emedium = out_22.1$samples_10$expansion_haul_numbers$length$iss$iss,
               N15_Emedium = out_22.1$samples_15$expansion_haul_numbers$length$iss$iss,
               N20_Emedium = out_22.1$samples_20$expansion_haul_numbers$length$iss$iss,
               N25_Emedium = out_22.1$samples_25$expansion_haul_numbers$length$iss$iss,
               N30_Emedium = out_22.1$samples_30$expansion_haul_numbers$length$iss$iss,
               N35_Emedium = out_22.1$samples_35$expansion_haul_numbers$length$iss$iss,
               N1_Efull = out_22.1$samples_1$expansion_haul_month_numbers$length$iss$iss,
               N5_Efull = out_22.1$samples_5$expansion_haul_month_numbers$length$iss$iss,
               N10_Efull = out_22.1$samples_10$expansion_haul_month_numbers$length$iss$iss,
               N15_Efull = out_22.1$samples_15$expansion_haul_month_numbers$length$iss$iss,
               N20_Efull = out_22.1$samples_20$expansion_haul_month_numbers$length$iss$iss,
               N25_Efull = out_22.1$samples_25$expansion_haul_month_numbers$length$iss$iss,
               N30_Efull = out_22.1$samples_30$expansion_haul_month_numbers$length$iss$iss,
               N35_Efull = out_22.1$samples_35$expansion_haul_month_numbers$length$iss$iss)

df2[grep("Enone", scenario)] %>% 
  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_Enone"])/df2$ISS[df2$scenario=="N20_Enone"],
                    type = "Enone",
                    .by = scenario) %>% 
  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -7)) -> df3.1

df2[grep("Emedium", scenario)] %>% 
  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_Emedium"])/df2$ISS[df2$scenario=="N20_Emedium"],
                    type = "Emedium",
                    .by = scenario) %>% 
  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -9)) -> df3.2

df2[grep("Efull", scenario)] %>% 
  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_Efull"])/df2$ISS[df2$scenario=="N20_Efull"],
                    type = "Efull",
                    .by = scenario) %>% 
  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -7)) -> df3.3

df3.1 %>% 
  tidytable::bind_rows(df3.2) %>% 
  tidytable::bind_rows(df3.3) %>% 
  tidytable::mutate(scenario = forcats::fct_inorder(scenario)) -> df4

df4 %>% 
  ggplot(aes(x = scenario, y = ISS.error*100)) +
  geom_boxplot(aes(fill = type)) +
  labs(x = "Scenario", y = "ISSB % Error") +
  theme_classic() +
  theme(legend.position = c(0.5, 0.2)) +
  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
  geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
  scale_y_continuous(breaks = seq(-100, 120, by = 10))

# Stats
df4 %>% filter(type=="trip", scenario=="N_0.25") %>% pull(ISS.error) %>% median
df4 %>% filter(type=="trip", scenario=="N_2.00") %>% pull(ISS.error) %>% median
df4 %>% filter(type=="haul", scenario=="N_0.25") %>% pull(ISS.error) %>% median
df4 %>% filter(type=="haul", scenario=="N_2.00") %>% pull(ISS.error) %>% median

### Samples VS Expantion TAKE 2: relative to unbiased control. Boxplots Together 1999-2023
```{r, fig.width=8}

out_22.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_22.1_ISS_200_iters_2024-12-25.RDS")

year = out_22.1$samples_1$expansion_NULL$length$iss$YEAR
samples_global = c(1, 5, 10, 15, 20, 25, 30, 35)
expansion_global = list(NULL, "haul_numbers", c("haul_numbers", "month_numbers"))
expansion_names_global = c("NULL", "haul_numbers", c("haul_month_numbers"))

df = tidytable(year = year,
               N1_Enone = out_22.1$samples_1$expansion_NULL$length$iss$iss,
               N5_Enone = out_22.1$samples_5$expansion_NULL$length$iss$iss,
               N10_Enone = out_22.1$samples_10$expansion_NULL$length$iss$iss,
               N15_Enone = out_22.1$samples_15$expansion_NULL$length$iss$iss,
               N20_Enone = out_22.1$samples_20$expansion_NULL$length$iss$iss,
               N25_Enone = out_22.1$samples_25$expansion_NULL$length$iss$iss,
               N30_Enone = out_22.1$samples_30$expansion_NULL$length$iss$iss,
               N35_Enone = out_22.1$samples_35$expansion_NULL$length$iss$iss,
               N1_Emedium = out_22.1$samples_1$expansion_haul_numbers$length$iss$iss,
               N5_Emedium = out_22.1$samples_5$expansion_haul_numbers$length$iss$iss,
               N10_Emedium = out_22.1$samples_10$expansion_haul_numbers$length$iss$iss,
               N15_Emedium = out_22.1$samples_15$expansion_haul_numbers$length$iss$iss,
               N20_Emedium = out_22.1$samples_20$expansion_haul_numbers$length$iss$iss,
               N25_Emedium = out_22.1$samples_25$expansion_haul_numbers$length$iss$iss,
               N30_Emedium = out_22.1$samples_30$expansion_haul_numbers$length$iss$iss,
               N35_Emedium = out_22.1$samples_35$expansion_haul_numbers$length$iss$iss,
               N1_Efull = out_22.1$samples_1$expansion_haul_month_numbers$length$iss$iss,
               N5_Efull = out_22.1$samples_5$expansion_haul_month_numbers$length$iss$iss,
               N10_Efull = out_22.1$samples_10$expansion_haul_month_numbers$length$iss$iss,
               N15_Efull = out_22.1$samples_15$expansion_haul_month_numbers$length$iss$iss,
               N20_Efull = out_22.1$samples_20$expansion_haul_month_numbers$length$iss$iss,
               N25_Efull = out_22.1$samples_25$expansion_haul_month_numbers$length$iss$iss,
               N30_Efull = out_22.1$samples_30$expansion_haul_month_numbers$length$iss$iss,
               N35_Efull = out_22.1$samples_35$expansion_haul_month_numbers$length$iss$iss)

df2 %>% 
  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_Efull"])/df2$ISS[df2$scenario=="N20_Efull"],
                    .by = scenario)

df2[grep("Enone", scenario)] %>% 
  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_Efull"])/df2$ISS[df2$scenario=="N20_Efull"],
                    type = "Enone",
                    .by = scenario) %>% 
  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -7)) -> df3.1

df2[grep("Emedium", scenario)] %>% 
  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_Efull"])/df2$ISS[df2$scenario=="N20_Efull"],
                    type = "Emedium",
                    .by = scenario) %>% 
  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -9)) -> df3.2

df2[grep("Efull", scenario)] %>% 
  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_Efull"])/df2$ISS[df2$scenario=="N20_Efull"],
                    type = "Efull",
                    .by = scenario) %>% 
  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -7)) -> df3.3

df3.1 %>% 
  tidytable::bind_rows(df3.2) %>% 
  tidytable::bind_rows(df3.3) %>% 
  tidytable::mutate(scenario = forcats::fct_inorder(scenario)) -> df4

df4 %>% 
  ggplot(aes(x = scenario, y = ISS.error*100)) +
  geom_boxplot(aes(fill = type)) +
  labs(x = "Scenario", y = "ISSB % Error") +
  theme_classic() +
  theme(legend.position = c(0.5, 0.2)) +
  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
  geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
  scale_y_continuous(breaks = seq(-100, 120, by = 10), limits = c(-100, 120))

# Stats
df4 %>% filter(type=="trip", scenario=="N_0.25") %>% pull(ISS.error) %>% median
df4 %>% filter(type=="trip", scenario=="N_2.00") %>% pull(ISS.error) %>% median
df4 %>% filter(type=="haul", scenario=="N_0.25") %>% pull(ISS.error) %>% median
df4 %>% filter(type=="haul", scenario=="N_2.00") %>% pull(ISS.error) %>% median

### Samples VS Haul. Boxplots Together 1999-2023
```{r, fig.width=8}

out_24.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_24.1_ISS_200_iters_2025-01-02.RDS")

year = out_24.1$samples_1$trip_0.25$length$iss$YEAR
samples_global = c(1, 5, 10, 15, 20, 25, 30, 35)
proportion_global = c(0.25, 0.50, 0.75, 1.25, 1.50, 1.75, 2.00)

df = tidytable(year = year,
               N1_H0.75 = out_24.1$samples_1$trip_0.75$length$iss$iss,
               N5_H0.75 = out_24.1$samples_5$trip_0.75$length$iss$iss,
               N10_H0.75 = out_24.1$samples_10$trip_0.75$length$iss$iss,
               N15_H0.75 = out_24.1$samples_15$trip_0.75$length$iss$iss,
               N20_H0.75 = out_24.1$samples_20$trip_0.75$length$iss$iss,
               N25_H0.75 = out_24.1$samples_25$trip_0.75$length$iss$iss,
               N30_H0.75 = out_24.1$samples_30$trip_0.75$length$iss$iss,
               N35_H0.75 = out_24.1$samples_35$trip_0.75$length$iss$iss,
               N1_H1.0 = out_22.1$samples_1$expansion_haul_month_numbers$length$iss$iss,
               N5_H1.0 = out_22.1$samples_5$expansion_haul_month_numbers$length$iss$iss,
               N10_H1.0 = out_22.1$samples_10$expansion_haul_month_numbers$length$iss$iss,
               N15_H1.0 = out_22.1$samples_15$expansion_haul_month_numbers$length$iss$iss,
               N20_H1.0 = out_22.1$samples_20$expansion_haul_month_numbers$length$iss$iss,
               N25_H1.0 = out_22.1$samples_25$expansion_haul_month_numbers$length$iss$iss,
               N30_H1.0 = out_22.1$samples_30$expansion_haul_month_numbers$length$iss$iss,
               N35_H1.0 = out_22.1$samples_35$expansion_haul_month_numbers$length$iss$iss,
               N1_H1.25 = out_24.1$samples_1$trip_1.25$length$iss$iss,
               N5_H1.25 = out_24.1$samples_5$trip_1.25$length$iss$iss,
               N10_H1.25 = out_24.1$samples_10$trip_1.25$length$iss$iss,
               N15_H1.25 = out_24.1$samples_15$trip_1.25$length$iss$iss,
               N20_H1.25 = out_24.1$samples_20$trip_1.25$length$iss$iss,
               N25_H1.25 = out_24.1$samples_25$trip_1.25$length$iss$iss,
               N30_H1.25 = out_24.1$samples_30$trip_1.25$length$iss$iss,
               N35_H1.25 = out_24.1$samples_35$trip_1.25$length$iss$iss)

df2[grep("H0.75", scenario)] %>% 
  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H0.75"])/df2$ISS[df2$scenario=="N20_H0.75"],
                    type = "H0.75",
                    .by = scenario) %>% 
  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -7)) -> df3.1

df2[grep("H1.0", scenario)] %>% 
  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H1.0"])/df2$ISS[df2$scenario=="N20_H1.0"],
                    type = "H1.0",
                    .by = scenario) %>% 
  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -6)) -> df3.2

df2[grep("H1.25", scenario)] %>% 
  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H1.25"])/df2$ISS[df2$scenario=="N20_H1.25"],
                    type = "H1.25",
                    .by = scenario) %>% 
  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -7)) -> df3.3

df3.1 %>% 
  tidytable::bind_rows(df3.2) %>% 
  tidytable::bind_rows(df3.3) %>% 
  tidytable::mutate(scenario = forcats::fct_inorder(scenario)) -> df4

df4 %>% 
  ggplot(aes(x = scenario, y = ISS.error*100)) +
  geom_boxplot(aes(fill = type)) +
  labs(x = "Scenario", y = "ISSB % Error") +
  theme_classic() +
  theme(legend.position = c(0.5, 0.2)) +
  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
  geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
  scale_y_continuous(breaks = seq(-100, 120, by = 10))

# Stats
df4 %>% filter(type=="trip", scenario=="N_0.25") %>% pull(ISS.error) %>% median
df4 %>% filter(type=="trip", scenario=="N_2.00") %>% pull(ISS.error) %>% median
df4 %>% filter(type=="haul", scenario=="N_0.25") %>% pull(ISS.error) %>% median
df4 %>% filter(type=="haul", scenario=="N_2.00") %>% pull(ISS.error) %>% median

### Samples VS Haul. Boxplots Together 1999-2023. sub-sample range
```{r, fig.width=8}

out_24.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_24.1_ISS_200_iters_2025-01-02.RDS")

year = out_24.1$samples_1$trip_0.25$length$iss$YEAR
samples_global = c(1, 5, 10, 15, 20, 25, 30, 35)
proportion_global = c(0.25, 0.50, 0.75, 1.25, 1.50, 1.75, 2.00)

df = tidytable(year = year,
               N1_H0.5 = out_24.1$samples_1$trip_0.5$length$iss$iss,
               N5_H0.5 = out_24.1$samples_5$trip_0.5$length$iss$iss,
               N10_H0.5 = out_24.1$samples_10$trip_0.5$length$iss$iss,
               N15_H0.5 = out_24.1$samples_15$trip_0.5$length$iss$iss,
               N20_H0.5 = out_24.1$samples_20$trip_0.5$length$iss$iss,
               N25_H0.5 = out_24.1$samples_25$trip_0.5$length$iss$iss,
               N30_H0.5 = out_24.1$samples_30$trip_0.5$length$iss$iss,
               N35_H0.5 = out_24.1$samples_35$trip_0.5$length$iss$iss,
               N1_H0.75 = out_24.1$samples_1$trip_0.75$length$iss$iss,
               N5_H0.75 = out_24.1$samples_5$trip_0.75$length$iss$iss,
               N10_H0.75 = out_24.1$samples_10$trip_0.75$length$iss$iss,
               N15_H0.75 = out_24.1$samples_15$trip_0.75$length$iss$iss,
               N20_H0.75 = out_24.1$samples_20$trip_0.75$length$iss$iss,
               N25_H0.75 = out_24.1$samples_25$trip_0.75$length$iss$iss,
               N30_H0.75 = out_24.1$samples_30$trip_0.75$length$iss$iss,
               N35_H0.75 = out_24.1$samples_35$trip_0.75$length$iss$iss,
               N1_H1.0 = out_22.1$samples_1$expansion_haul_month_numbers$length$iss$iss,
               N5_H1.0 = out_22.1$samples_5$expansion_haul_month_numbers$length$iss$iss,
               N10_H1.0 = out_22.1$samples_10$expansion_haul_month_numbers$length$iss$iss,
               N15_H1.0 = out_22.1$samples_15$expansion_haul_month_numbers$length$iss$iss,
               N20_H1.0 = out_22.1$samples_20$expansion_haul_month_numbers$length$iss$iss,
               N25_H1.0 = out_22.1$samples_25$expansion_haul_month_numbers$length$iss$iss,
               N30_H1.0 = out_22.1$samples_30$expansion_haul_month_numbers$length$iss$iss,
               N35_H1.0 = out_22.1$samples_35$expansion_haul_month_numbers$length$iss$iss,
               N1_H1.25 = out_24.1$samples_1$trip_1.25$length$iss$iss,
               N5_H1.25 = out_24.1$samples_5$trip_1.25$length$iss$iss,
               N10_H1.25 = out_24.1$samples_10$trip_1.25$length$iss$iss,
               N15_H1.25 = out_24.1$samples_15$trip_1.25$length$iss$iss,
               N20_H1.25 = out_24.1$samples_20$trip_1.25$length$iss$iss,
               N25_H1.25 = out_24.1$samples_25$trip_1.25$length$iss$iss,
               N30_H1.25 = out_24.1$samples_30$trip_1.25$length$iss$iss,
               N35_H1.25 = out_24.1$samples_35$trip_1.25$length$iss$iss)

df2[grep("H0.5", scenario)] %>% 
  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H0.5"])/df2$ISS[df2$scenario=="N20_H0.5"],
                    type = "0.5",
                    .by = scenario) %>% 
  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -6)) -> df3.01

df2[grep("H0.75", scenario)] %>% 
  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H0.75"])/df2$ISS[df2$scenario=="N20_H0.75"],
                    type = "0.75",
                    .by = scenario) %>% 
  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -7)) -> df3.1

df2[grep("H1.0", scenario)] %>% 
  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H1.0"])/df2$ISS[df2$scenario=="N20_H1.0"],
                    type = "1.0",
                    .by = scenario) %>% 
  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -6)) -> df3.2

df2[grep("H1.25", scenario)] %>% 
  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H1.25"])/df2$ISS[df2$scenario=="N20_H1.25"],
                    type = "1.25",
                    .by = scenario) %>% 
  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -7)) -> df3.3

df3.01 %>% 
  tidytable::bind_rows(df3.1) %>% 
  tidytable::bind_rows(df3.2) %>% 
  tidytable::bind_rows(df3.3) %>% 
  tidytable::mutate(scenario = forcats::fct_inorder(scenario)) -> df4
df4 -> df4.1.a

df4 %>% 
  ggplot(aes(x = scenario, y = ISS.error*100)) +
  geom_boxplot(aes(fill = type)) +
  labs(x = "Scenario", y = "ISSB % Error") +
  theme_classic() +
  theme(legend.position = c(0.5, 0.2)) +
  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
  geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
  scale_y_continuous(breaks = seq(-100, 120, by = 10))

df4 %>% 
  tidytable::filter(scenario %in% c("N5", "N10", "N15")) %>% 
  ggplot(aes(x = scenario, y = ISS.error*100)) +
  geom_boxplot(aes(fill = type)) +
  labs(x = "Scenario", y = "ISSB % Error") +
  theme_classic() +
  theme(legend.position = c(0.5, 0.2)) +
  geom_hline(yintercept = -10, linetype = "dashed", color = "black") +
  geom_hline(yintercept = 10, linetype = "dashed", color = "black") +
  scale_y_continuous(breaks = seq(-100, 120, by = 10))

# Stats
df4 %>% filter(type=="trip", scenario=="N_0.25") %>% pull(ISS.error) %>% median
df4 %>% filter(type=="trip", scenario=="N_2.00") %>% pull(ISS.error) %>% median
df4 %>% filter(type=="haul", scenario=="N_0.25") %>% pull(ISS.error) %>% median
df4 %>% filter(type=="haul", scenario=="N_2.00") %>% pull(ISS.error) %>% median

### Samples VS Haul TAKE 2: relative to unbiased control. Boxplots Together 1999-2023. sub-sample range
```{r, fig.width=8}

out_24.1 = readRDS(file = "C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/paper_output/paper_scenario_24.1_ISS_200_iters_2025-01-02.RDS")

year = out_24.1$samples_1$trip_0.25$length$iss$YEAR
samples_global = c(1, 5, 10, 15, 20, 25, 30, 35)
proportion_global = c(0.25, 0.50, 0.75, 1.25, 1.50, 1.75, 2.00)

df = tidytable(year = year,
               N1_H0.5 = out_24.1$samples_1$trip_0.5$length$iss$iss,
               N5_H0.5 = out_24.1$samples_5$trip_0.5$length$iss$iss,
               N10_H0.5 = out_24.1$samples_10$trip_0.5$length$iss$iss,
               N15_H0.5 = out_24.1$samples_15$trip_0.5$length$iss$iss,
               N20_H0.5 = out_24.1$samples_20$trip_0.5$length$iss$iss,
               N25_H0.5 = out_24.1$samples_25$trip_0.5$length$iss$iss,
               N30_H0.5 = out_24.1$samples_30$trip_0.5$length$iss$iss,
               N35_H0.5 = out_24.1$samples_35$trip_0.5$length$iss$iss,
               N1_H0.75 = out_24.1$samples_1$trip_0.75$length$iss$iss,
               N5_H0.75 = out_24.1$samples_5$trip_0.75$length$iss$iss,
               N10_H0.75 = out_24.1$samples_10$trip_0.75$length$iss$iss,
               N15_H0.75 = out_24.1$samples_15$trip_0.75$length$iss$iss,
               N20_H0.75 = out_24.1$samples_20$trip_0.75$length$iss$iss,
               N25_H0.75 = out_24.1$samples_25$trip_0.75$length$iss$iss,
               N30_H0.75 = out_24.1$samples_30$trip_0.75$length$iss$iss,
               N35_H0.75 = out_24.1$samples_35$trip_0.75$length$iss$iss,
               N1_H1.0 = out_22.1$samples_1$expansion_haul_month_numbers$length$iss$iss,
               N5_H1.0 = out_22.1$samples_5$expansion_haul_month_numbers$length$iss$iss,
               N10_H1.0 = out_22.1$samples_10$expansion_haul_month_numbers$length$iss$iss,
               N15_H1.0 = out_22.1$samples_15$expansion_haul_month_numbers$length$iss$iss,
               N20_H1.0 = out_22.1$samples_20$expansion_haul_month_numbers$length$iss$iss,
               N25_H1.0 = out_22.1$samples_25$expansion_haul_month_numbers$length$iss$iss,
               N30_H1.0 = out_22.1$samples_30$expansion_haul_month_numbers$length$iss$iss,
               N35_H1.0 = out_22.1$samples_35$expansion_haul_month_numbers$length$iss$iss,
               N1_H1.25 = out_24.1$samples_1$trip_1.25$length$iss$iss,
               N5_H1.25 = out_24.1$samples_5$trip_1.25$length$iss$iss,
               N10_H1.25 = out_24.1$samples_10$trip_1.25$length$iss$iss,
               N15_H1.25 = out_24.1$samples_15$trip_1.25$length$iss$iss,
               N20_H1.25 = out_24.1$samples_20$trip_1.25$length$iss$iss,
               N25_H1.25 = out_24.1$samples_25$trip_1.25$length$iss$iss,
               N30_H1.25 = out_24.1$samples_30$trip_1.25$length$iss$iss,
               N35_H1.25 = out_24.1$samples_35$trip_1.25$length$iss$iss)

df2[grep("H0.5", scenario)] %>% 
  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H1.0"])/df2$ISS[df2$scenario=="N20_H1.0"],
                    type = "0.5",
                    .by = scenario) %>% 
  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -6)) -> df3.01

df2[grep("H0.75", scenario)] %>% 
  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H1.0"])/df2$ISS[df2$scenario=="N20_H1.0"],
                    type = "0.75",
                    .by = scenario) %>% 
  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -7)) -> df3.1

df2[grep("H1.0", scenario)] %>% 
  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H1.0"])/df2$ISS[df2$scenario=="N20_H1.0"],
                    type = "1.0",
                    .by = scenario) %>% 
  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -6)) -> df3.2

df2[grep("H1.25", scenario)] %>% 
  tidytable::mutate(ISS.error = (ISS - df2$ISS[df2$scenario=="N20_H1.0"])/df2$ISS[df2$scenario=="N20_H1.0"],
                    type = "1.25",
                    .by = scenario) %>% 
  tidytable::mutate(scenario = str_sub(scenario, start = 1, end = -7)) -> df3.3

df3.01 %>% 
  tidytable::bind_rows(df3.1) %>% 
  tidytable::bind_rows(df3.2) %>% 
  tidytable::bind_rows(df3.3) %>% 
  tidytable::mutate(scenario = forcats::fct_inorder(scenario)) -> df4
df4 -> df4.1.b
